Multiple Kernelized Correlation Filters based High Speed Target Following

### 2017-04-09 draft.tex
Revised introduction a bit.

\documentclass[10pt,twocolumn,letterpaper]{article}
\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools} % mathtools builds on and extends amsmath package
\usepackage{algorithm}		% http://ctan.org/pkg/algorithms
\usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.

@@

\author{Burak Uzkent\\
Rochester Institute of Technology\\
{\tt\small bxu2522@@rit.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
YoungWoo Seo\\
Affiliation\\
{\tt\small yseo@autelrobotics.edu}
}

@@

The tracking-by-detection methods have recently emerged as robust,
powerful, and highly discriminative trackers replacing the preceding
generative trackers that focused on only target modeling. Some of the
recent tracking-by-detection algorithms are
Tracking-Learning-Detection \cite{kalal2012tracking}, Multiple
Instance Learning \cite{babenko2009visual}, Correlation Filter based
trackers \cite{bolme2010visual,henriques2015high}, and Struck
\cite{hare2012efficient}. These tracking-by-detection methods train an
object-specific classifier on the fly with the focus of discriminating
the target from the background. Learning an object-specific classifier
in an online manner can better handle challenging scenarios with the
cost of increased complexity. In order to train a classifier, one need
positive and negative samples. Randomly collecting negative samples
from the background area can be one straightforward way of building
training data to train the classifier. However, there can be two
issues in this framework. First, the randomly collected samples can
have large correlation resulting in a weak classifier. Also, such
framework is not feasible for real-time tracking as the number of
samples gradually increases. Most of the tracking-by-detection
algorithms focus on efficient incremental update of a classifier
together with more useful background sampling.

>>>>

\documentclass[10pt,twocolumn,letterpaper]{article}
\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools} % mathtools builds on and extends amsmath package
\usepackage{algorithm}		% http://ctan.org/pkg/algorithms
\usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
\usepackage{comment}

@@

\author{Burak Uzkent\\
Rochester Institute of Technology\\
{\tt\small bxu2522@@rit.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
YoungWoo Seo\\
Affiliation\\
{\tt\small youngwoo.blank.seo@gmail.com}
}

@@

The tracking-by-detection methods have recently used extensively as a
robust, powerful, and highly discriminative vision-based, object
tracking method replacing the preceding, generative object tracking
methods that primarily concerned about learning the appearance of the
target. The recent examples of the tracking-by-detection algorithms
include Tracking-Learning-Detection \cite{kalal2012tracking}, Multiple
Instance Learning \cite{babenko2009visual}, Correlation Filter based
trackers \cite{bolme2010visual,henriques2015high}, and Struck
\cite{hare2012efficient}. These tracking-by-detection methods learn
the model of the target's appearance on the fly while discriminating
the target from the background.

{\it Burak: It isn't clear what you're getting at here} Learning
an object-specific classifier in an online manner can better handle
challenging scenarios with the cost of increased complexity.

To train a (binary) classifier to detect the target at every frame,
the classifier needs positive and negative examples. In a typical set
up, a positive example is assumed to be given whereas a set of
negative examples can be randomly collected from the background around
the given positive example. Such a typical setup for a
tracking-by-detection method might have two issues related to its
performance: Firstly, the appearance of the randomly sampled negative
examples might be highly correlated with that of positive one,
resulting in ambiguous boundary between positive and negative
classes. Secondly for a real-time tracking, such a setup would not be
feasible for the practice because the number of training data
gradually increases. Due to these issues, most of the
tracking-by-detection methods focus on efficiently handling
incremental update of the learned classifier and on collecting a
small, but informative negative examples.
\begin{comment}
However, there can be two issues in this framework. First,
the randomly collected samples can have large correlation resulting in
a weak classifier. Also, such framework is not feasible for real-time
tracking as the number of samples gradually increases. Most of the
tracking-by-detection algorithms focus on efficient incremental update
of a classifier together with more useful background sampling.
\end{comment}
